---
title: "Figure 5 - Delay between sensors"
output: html_notebook
---

Figure 5. Comparison of the delay of the different model of sensors determined by calculating the
maximum R2 obtained with the DustTrak by applying different time lag to the readings of each of the
sensor tested, by model of sensor and by experiment conducted. The box and whisker plot horizontal
lines represent, from bottom to top, the 1st quartile, the median and the 3rd quartile. The vertical lines
represent the data points that fall within 1.5 times the interquartile range below the 1st quartile and
above the 3rd quartile. Values outside these range are considered as outliers and plotted as points (none
are present here).


```{r setup}


require(openair)
require(splitstackshape)
require(ggpubr)
source("utilities.R")
source("variables.R")

df <- prepare_sensor_data(sensor_raw_file, cdt) %>%
  select(date, sensor, site, PM25, exp, source, variation)


dusttrak <- prepare_dusttrak_data(dusttrak_file, cdt)


```


Calculate the R2 obtained between the sensors and the DustTrak, by adding a delay between 0-100s to the readings of the sensors.
```{r, warning=FALSE}
#Initialise
delay <- 0
res <- df %>%
    filter(sensor !="SHT35", exp != "") %>%
  mutate(date = ymd_hms(date) - seconds(delay)) %>%
  group_by(sensor, exp) %>%
  nest() %>%
dplyr::mutate(regression = map(data, ~clean_regression(df =.x,dusttrak = dusttrak, 0))) %>%
  unnest(regression, .drop = TRUE) %>%
  mutate(delay = delay)


for(delay in 1:100){
  df %>%
    filter(sensor !="SHT35", exp != "") %>%
  mutate(date = ymd_hms(date) - seconds(delay)) %>%
  group_by(sensor, date = make_datetime(year =  year(date), month = month(date), 
                                        day = day(date),hour = hour(date), min=minute(date), 
                                        sec = round2(second(date)/10,0)*10)) %>% 
    summarise_each(funs(mean(., na.rm = TRUE)), PM25) -> tmp
  tmp <- flag_cdt_data(tmp, cdt)
  tmp %>%
  group_by(sensor, exp) %>%
  nest() %>%
dplyr::mutate(regression = map(data, ~clean_regression(df =.x,dusttrak = dusttrak, 0))) %>%
  unnest(regression, .drop = TRUE) %>%
  mutate(delay = delay)->tmp
  res<-rbind(res,tmp)
  
}
#write.csv(select(res,-data), file = "delay_r_squared.csv")
```


```{r}


#res <-read.csv(file = "delay_r_squared.csv")
df2<-cSplit(indt=res,splitCols = c("sensor"),sep="-",direction="wide",drop=FALSE) %>%
  select(-sensor_2,-sensor_3)->df2


p<-df2 %>%
  filter(exp != "") %>%
  ggplot() +
  geom_line(aes(x=delay, y = r_squared_adjusted,group=sensor, colour = sensor)) +
  facet_grid(exp~sensor_1) +
  theme_bw() +
  ylab("Adjusted R2") +
  xlab("Delay (s)") +
  theme(strip.text.y = element_text(size = 6))

legend<-get_legend(p)
#p<-p+theme(legend.position = "none")
p
ggplotly(p)
#ggsave(p,filename="delay_evolution.svg")
#ggplotly(p)
```



```{r}

summary(res)

p<-df2 %>%
  group_by(sensor_1,sensor, exp) %>%
  filter(r_squared_adjusted == max(r_squared_adjusted)) %>%
  summarise(min_delay = min(delay), max_delay = max(delay))%>%
  filter(exp != "") %>%
  ggplot() +
  geom_boxplot(aes(x=exp,y=min_delay)) +
  #geom_point(aes(x=exp,y=min_delay))+
  facet_grid(~sensor_1)+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none") +
  scale_y_continuous(breaks = seq(0,100, by =5))
#ggsave(p,filename="delay_evolution_boxplot.svg",width = 7, height = 5)

ggplotly(p)

```

