---
title: "Figure 8 - Calibration of the sensors"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

Figure 8. Ratio of the maximum value of the peaks measured by the sensors against the maximum
value of the peaks measured by the DustTrak before and after calibration for each experiment. The box
and whisker plot horizontal lines represent, from bottom to top, the lower quartile, the median and the
upper quartile. The vertical lines are drawn to the smallest and the largest data point that fall within
1.5 times the interquartile range below the lower quartile and above the upper quartile respectively.
Values outside these range are considered as outliers and plotted as points.

```{r setup}

source("utilities.R")
source("variables.R")
require(ggplot2)
require(plotly)
require(cowplot)
require(splitstackshape)
require(ggpubr)
source("Table_2_rh_exploration.R")


```


```{r}

df <- prepare_sensor_data(sensor_delay_corrected, cdt)
dt <- prepare_dusttrak_data(dusttrak_file, cdt)

df %>%
  select(sensor, exp, source, date, PM25) %>%
  filter(sensor!="SHT35") %>%
  filter(exp!="") %>%
  group_by(exp, source, sensor) %>%
  nest() -> tmp

tmp %>%
  dplyr::mutate(regression = map(data, ~clean_regression(df =.x,dusttrak = dt, 0))) %>%
  unnest(regression, .drop=TRUE)  ->res



res<-cSplit(indt=res,splitCols = c("sensor"),sep="-",direction="wide",drop=FALSE) %>%
  select(-sensor_2,-sensor_3)->res

res <- res %>%
  flag_site_data(sensor_list)

res_rh_temp <- inner_join(res, summary_rh_temp, by = c("exp"))


#write.csv(select(res_rh_temp,-data), "C:/GitHub/AQ_analysis_lab/lm_no_enclosure_cdt_corr.csv")

res_rh_temp <- res_rh_temp %>%
  mutate(rh_median  = round2(rh_median,0))
```


```{r}
df %>% inner_join(select(res_rh_temp, sensor, exp, source, slope, intercept, slope_p_value), by = c("sensor", "exp", "source")) -> df_coeff

df_coeff %>% 
  mutate(PM25_corr = ifelse(slope_p_value<=0.05,(PM25-intercept)/slope), -999) %>%
  filter(PM25_corr != -999) -> df_calibrated

df_calibrated<-cSplit(indt=df_calibrated,splitCols = c("sensor"),sep="-",direction="wide",drop=FALSE) %>%
  select(-sensor_2,-sensor_3)
```

What does it looks like?

```{r}
p_opcr1 <- ggplot()+
  geom_line(data = filter(df_calibrated, sensor_1=="OPCR1", exp != ""),
            aes(x = date, y = PM25_corr, group = sensor, colour = sensor, 
                text = paste0("Box: ", site,
                              "<br>Exp: ", exp,
                              "<br>Source: ", source))) +
  labs(y = "PM2.5 (ug/m3)") +
  geom_line(data = filter(dt, exp != ""), aes(x = date,y = pm2.5), colour = "red", linetype = "dashed")+
  scale_x_datetime() + theme_bw() + ggtitle("OPCR1") + theme(plot.title = element_text(hjust = 0.5))+facet_wrap(~exp, ncol = 1, scales = "free_x")


p_pms5003 <- ggplot()+
  geom_line(data = filter(df_calibrated, sensor_1=="PMS5003", exp != ""),
            aes(x = date, y = PM25_corr, group = sensor, colour = sensor, 
                text = paste0("Box: ", site,
                              "<br>Exp: ", exp,
                              "<br>Source: ", source))) +
  labs(y = "PM2.5 (ug/m3)") +
  geom_line(data = filter(dt, exp != ""), aes(x = date,y = pm2.5), colour = "red", linetype = "dashed")+
  scale_x_datetime() + theme_bw() + ggtitle("PMS5003") + theme(plot.title = element_text(hjust = 0.5))+facet_wrap(~exp, ncol = 1, scales = "free_x")

p_sds018 <- ggplot()+
  geom_line(data = filter(df_calibrated, sensor_1=="SDS018", exp != ""),
            aes(x = date, y = PM25_corr, group = sensor, colour = sensor, 
                text = paste0("Box: ", site,
                              "<br>Exp: ", exp,
                              "<br>Source: ", source))) +
  labs(y = "PM2.5 (ug/m3)") +
  geom_line(data = filter(dt, exp != ""), aes(x = date,y = pm2.5), colour = "red", linetype = "dashed")+
  scale_x_datetime() + theme_bw() + ggtitle("SDS018") + theme(plot.title = element_text(hjust = 0.5))+facet_wrap(~exp, ncol = 1, scales = "free_x")

p_sps030 <- ggplot()+
  geom_line(data = filter(df_calibrated, sensor_1=="SPS030", exp != ""),
            aes(x = date, y = PM25_corr, group = sensor, colour = sensor, 
                text = paste0("Box: ", site,
                              "<br>Exp: ", exp,
                              "<br>Source: ", source))) +
  labs(y = "PM2.5 (ug/m3)") +
  geom_line(data = filter(dt, exp != ""), aes(x = date,y = pm2.5), colour = "red", linetype = "dashed")+
  scale_x_datetime() + theme_bw() + ggtitle("SPS030") + theme(plot.title = element_text(hjust = 0.5))+facet_wrap(~exp, ncol = 1, scales = "free_x")

p_hpma <- ggplot()+
  geom_line(data = filter(df_calibrated, sensor_1=="HPMA115S0", exp != ""),
            aes(x = date, y = PM25_corr, group = sensor, colour = sensor, 
                text = paste0("Box: ", site,
                              "<br>Exp: ", exp,
                              "<br>Source: ", source))) +
  labs(y = "PM2.5 (ug/m3)") +
  geom_line(data = filter(dt, exp != ""), aes(x = date,y = pm2.5), colour = "red", linetype = "dashed")+
  scale_x_datetime() + theme_bw() + ggtitle("HPMA115S0") + theme(plot.title = element_text(hjust = 0.5))+facet_wrap(~exp, ncol = 1, scales = "free_x")

ggplotly(p_opcr1, dynamicTicks = TRUE)
ggplotly(p_pms5003, dynamicTicks = TRUE)
ggplotly(p_sds018, dynamicTicks = TRUE)
ggplotly(p_sps030, dynamicTicks = TRUE)
ggplotly(p_hpma, dynamicTicks = TRUE)
```

Now we extract the peaks.

```{r}
peaks<-readRDS(file="datasets/peaks_characteristics.rds") 


res <- df_calibrated %>%
    filter(date>=as.POSIXct(paste("2019-09-05", peaks[1,]$Start),tz="UTC"), date<=as.POSIXct(paste("2019-09-05", peaks[1,]$End),tz="UTC")) %>%
    group_by(sensor) %>%
  filter(PM25>=1) %>%
  summarise(max_value = max(PM25_corr)) %>%
    mutate(Experiment = peaks[1,]$Experiment, Source = peaks[1,]$Source, Variation= peaks[1,]$Variation, Number = peaks[1,]$Number)
for(row in 2:nrow(peaks)){
  df_calibrated %>%
    filter(date>=as.POSIXct(paste("2019-09-05", peaks[row,]$Start),tz="UTC"), date<=as.POSIXct(paste("2019-09-05", peaks[row,]$End),tz="UTC")) %>%
    group_by(sensor) %>%
      filter(PM25>=1) %>%
  summarise(max_value = max(PM25_corr)) %>%
    mutate(Experiment = peaks[row,]$Experiment, Source = peaks[row,]$Source, Variation= peaks[row,]$Variation, Number = peaks[row,]$Number) -> tmp
  res<-rbind(res,tmp)
  
} 
res %>%
  inner_join(peaks, by=c("Source", "Experiment", "Variation", "Number")) ->res_bind

res_bind<-res_bind %>%
  mutate(ratio = max_value/Concentration)



res_bin<-cSplit(indt=res_bind,splitCols = c("sensor"),sep="-",direction="wide",drop=FALSE) %>%
  select(-sensor_2,-sensor_3)


```


# Compare with uncalibrated data

```{r}

res <- df %>%
  filter(date >= as.POSIXct(paste("2019-09-05", peaks[1,]$Start), tz = "UTC"), 
         date <= as.POSIXct(paste("2019-09-05", peaks[1,]$End), tz = "UTC")) %>%
  group_by(sensor) %>%
  filter(PM25 >= 1) %>%
  summarise(max_value = max(PM25)) %>%
  mutate(Experiment = peaks[1, ]$Experiment, Source = peaks[1, ]$Source, Variation = peaks[1, ]$Variation, Number = peaks[1, ]$Number)
for(row in 2:nrow(peaks)){
  df %>%
    filter(date >= as.POSIXct(paste("2019-09-05", peaks[row, ]$Start), tz = "UTC"), 
           date <= as.POSIXct(paste("2019-09-05", peaks[row, ]$End), tz = "UTC")) %>%
    group_by(sensor) %>%
    filter(PM25 >= 1) %>%
  summarise(max_value = max(PM25)) %>%
  mutate(Experiment = peaks[row, ]$Experiment, Source = peaks[row, ]$Source, 
         Variation= peaks[row, ]$Variation, Number = peaks[row, ]$Number) -> tmp
  res<-rbind(res,tmp)
  
} 
res_bind_uncalibrated<- res %>%
  inner_join(peaks, by = c("Source", "Experiment", "Variation", "Number"))  %>%
  mutate(ratio = max_value/Concentration)


res_bind$status <- "Calibrated"
res_bind_uncalibrated$status <- "Not Calibrated"
res_comparison <- rbind(res_bind, res_bind_uncalibrated)

df2<-cSplit(indt=res_comparison,splitCols = c("sensor"),sep="-",direction="wide",drop=FALSE)

df2 %>%
  select(-sensor_2,-sensor_3)->res_comparison



```

```{r}

res_comparison$sensor_1 <- factor(res_comparison$sensor_1, levels = c("PMS5003", "SPS030", "HPMA115S0", "SDS018", "OPCR1"))

res_comparison$status <- factor(res_comparison$status, levels = c("Not Calibrated", "Calibrated"))
res_comparison %>%
  filter(Variation == "Peak") %>%
  ggplot(aes(x=Experiment,y=ratio,fill=status)) + 
   geom_boxplot(width=0.8,position=position_dodge(width = 0.8),alpha=0.8,lwd=0.3,fatten=0.8,outlier.size = 0.8,outlier.alpha=0.5,outlier.stroke=0)+
  facet_wrap(sensor_1~Source,ncol=4)+ylab("Ratio sensor/dusttrak")+theme_bw()+
  scale_y_continuous(breaks=pretty(c(-1,6), n=14),sec.axis = dup_axis(name=NULL))+
  theme(axis.text.x = element_text(angle=90,size = 6))->p
p_legend<-get_legend(p)

plot_grid(p_legend)

p<-p+theme(legend.position = "none")
p<-p+  theme(panel.spacing = unit(0, "lines")) +
  theme(plot.margin = unit(c(0,0,0,0), "lines"))
p
#ggsave(p,filename = "ratio_comparison_spacing.svg",unit = "mm", width= 180, height = 240)
#(as_ggplot(p_legend),filename = "ratio_comparison_legend.svg",unit = "mm", width= 180, height = 240)


```




