---
title: "Limit of detection - blank conditions"
output: html_notebook
---

This notebook generates the 3rd figure and table of the paper.

Figure 3. Lower limit of detection of the different models of sensors, under blank conditions, reported
in PM2.5 μg/m3. The box and whisker plot horizontal lines represent, from bottom to top, the lower
quartile, the median and the upper quartile. The vertical lines are drawn to the smallest and the largest
data point that fall within 1.5 times the interquartile range below the lower quartile and above the
upper quartile respectively. Each dot represents the value obtained by individual sensors.

Table 3. Range of the lower limit of detection of Alphasense OPC-R1, Plantower PMS5003 and Sensirion
SPS030, under blank condition, reported in number of particles per ml

```{r message=FALSE, warning=FALSE}
require(splitstackshape)
require(openair)
source("variables.R")
source("utilities.R")
```

We use the data from the blank experiment.

```{r}
df <- readRDS(sensor_blank) %>%
  filter(date>=as.POSIXct("2019-08-26 13:06:00",tz="UTC"),date<=as.POSIXct("2019-08-26 14:34:00",tz="UTC")) %>% # time start and end of experiment.
  filter(!(sensor %in% c("HPMA115S0-R0B174843287", "OPCR1-178871513", "OPCR1-178872113", "HPMA115S0-T0B190515497"))) # remove the faulty sensors.

df %>%
  group_by(sensor) %>%
  summarise(lod=3*sd(PM25,na.rm=TRUE))->sensor_lod
sensor_lod

# Extract the sensor type from the sensor_id and store it in sensor_1
df2<-cSplit(indt=sensor_lod,splitCols = c("sensor"),sep="-",direction="wide",drop=FALSE) %>%
  select(-sensor_2,-sensor_3)

p<-df2 %>%
  filter(lod<=15)%>%
  ggplot()+geom_boxplot(aes(x=sensor_1, y = lod),outlier.shape = NA)+geom_point(aes(x=sensor_1, y = lod),position = position_jitter(w = 0.2, h = 0))+ylab(quickText("Lower limit of detection PM2.5 (ug/m3)"))+xlab("Model of sensor") +theme_bw()
p

#ggsave(filename = "lod_paper.svg",plot = p,width = 5,height = 5)

```


# Particle numbers

```{r}

df %>% 
  filter(grepl("PMS5003",sensor)) %>%
  group_by(sensor) %>%
  mutate(total = gr03um + gr05um + gr10um + gr25um + gr50um + gr100um) %>%
  group_by(sensor) %>%
  summarise(lod_total = 3*sd(total, na.rm = TRUE)/100
            )->pms5003_lod
  #Compare this result to the OPS, not the DustTrak + the Nanotracer.
# integrate the results from the Nanotracer to the graphs I already have: Dashboard?
  
pms5003_lod

```

For the OPCR1

```{r}

df %>% 
  filter(grepl("OPCR1",sensor)) %>%
  group_by(sensor) %>%
  mutate(total = Bin1 + Bin2 + Bin3 + Bin4 + Bin5 + Bin6 + Bin7 + Bin8 + Bin9 + Bin10 + Bin11 + Bin12 + Bin13 + Bin14 + Bin15) %>%
  mutate(total_pn = total / SFR * SamplingPeriod) %>% # Convert to particles/ml
  group_by(sensor) %>%
  summarise(lod_total = 3*sd(total_pn, na.rm = TRUE)
            )->opcr1_lod
  #Compare this result to the OPS, not the DustTrak + the Nanotracer.
# integrate the results from the Nanotracer to the graphs I already have: Dashboard?
  
opcr1_lod


```


For the SPS030

```{r}

df %>% 
  filter(grepl("SPS030",sensor)) %>%
  group_by(sensor) %>%
  mutate(total =n05+n1+n10+n25+n4) %>%
  group_by(sensor) %>%
  summarise(lod_total = 3*sd(total, na.rm = TRUE)
            )->sps030_lod
  
sps030_lod



```

