---
title: "Slope and R squared per source - Figure 6 and 7"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

Figure 6. R2 of the linear regression between the readings of the sensors and the DustTrak for different
level of relative humidity (each level of relative humidity corresponds to experiments 1 to 5), for candle
and incense generated concentrations of PM2.5 (peaks and stable concentrations not differentiated). For
each graph, the colours correspond to the sensors of the model tested. Only the points with a p-value
<0.05 have been considered. The box and whisker plot horizontal lines represent, from bottom to top,
the lower quartile, the median and the upper quartile. The vertical lines are drawn to the smallest and
the largest data point that fall within 1.5 times the interquartile range below the lower quartile and
above the upper quartile respectively. Values outside these range are considered as outliers.


Figure 7. Slopes of the linear regression between the readings of the sensors and the DustTrak (y=sensor,
x=DustTrak) for different level of relative humidity (each level of relative humidity corresponds to
experiments 1 to 5), for candle and incense generated concentrations of PM2.5 (peaks and stable
concentrations not differentiated). For each graph, the colours correspond to the sensors of the model
tested. The colours are consistent with Figure 6. Only the points with a p-value <0.05 have been
considered. The box and whisker plot horizontal lines represent, from bottom to top, the lower quartile,
the median and the upper quartile. The vertical lines are drawn to the smallest and the largest data
point that fall within 1.5 times the interquartile range below the lower quartile and above the upper
quartile respectively. Values outside these range are considered as outliers.

```{r setup}

source("utilities.R")
source("variables.R")
require(ggplot2)
require(plotly)
require(cowplot)

source("Table_2_rh_exploration.R")


```


```{r}

df <- prepare_sensor_data(sensor_delay_corrected, cdt)
dt <- prepare_dusttrak_data(dusttrak_file, cdt)

df %>%
  select(sensor, exp, source, date, PM25) %>%
  filter(sensor!="SHT35") %>%
  filter(exp!="") %>%
  group_by(exp, source, sensor) %>%
  nest() -> tmp

tmp %>%
  dplyr::mutate(regression = map(data, ~clean_regression(df = .x, dusttrak = dt, 0))) %>%
  unnest(regression, .drop=TRUE)  ->res



res <- cSplit(indt = res,splitCols = c("sensor"), sep = "-", direction = "wide", drop = FALSE) %>%
  select(-sensor_2, -sensor_3)

res <- res %>%
  flag_site_data(sensor_list)

res_rh_temp <- inner_join(res, summary_rh_temp, by = c("exp"))


#write.csv(select(res_rh_temp,-data), "C:/GitHub/AQ_analysis_lab/lm_no_enclosure_cdt_corr.csv")

res_rh_temp <- res_rh_temp %>%
  mutate(rh_median  = round2(rh_median,0))
```

# Slope SIG with Box and Whisker

```{r}

customTheme<-theme_bw()+theme(legend.position = "none", axis.title.x=element_blank(), axis.title.y=element_blank(), plot.title = element_text(hjust = 0.5))

p_pms<-filter(res_rh_temp,slope_p_value<=0.05) %>%
  filter(grepl("PMS5003",sensor)) %>%
  ggplot() +    
  geom_boxplot(aes(x = rh_median,y=slope,group=rh_median), size=0.5, fatten=0.8) +
  geom_line(aes(x = rh_median,y=slope, group = sensor, color = sensor,alpha=0.9)) +
  ylim(c(0,1.2))+
  facet_grid(~source) +
  ylab("Slope") + 
  ggtitle("PMS5003") + 
  xlab("Relative humidity (%)") +
  customTheme

p_pms

p_opcr1<-filter(res_rh_temp,slope_p_value<=0.05) %>%
  filter(grepl("OPCR1",sensor)) %>%
  ggplot()+    
  geom_boxplot(aes(x = rh_median,y=slope,group=rh_median), size=0.5, fatten=0.8)+
  geom_line(aes(x = rh_median,y=slope, group = sensor, color = sensor,alpha=0.9))+
  facet_grid(~source) +
  ylab("Slope") + 
  ggtitle("OPCR1") + 
  xlab("Relative humidity (%)") +
  customTheme

p_sps<-filter(res_rh_temp, slope_p_value<=0.05) %>%
  filter(grepl("SPS030",sensor)) %>%
  ggplot()+    
  geom_boxplot(aes(x = rh_median, y = slope, group = rh_median), size=0.5, fatten=0.8)+
  geom_line(aes(x = rh_median, y = slope, group = sensor, color = sensor, alpha = 0.9))+
  ylim(c(0,1.2)) +
  facet_grid(~source) +
  ylab("Slope") + 
  ggtitle("SPS030") +
  xlab("Relative humidity (%)") +
  customTheme


p_sds<-filter(res_rh_temp, slope_p_value <= 0.05) %>%
  filter(grepl("SDS018", sensor)) %>%
  ggplot() +    
  geom_boxplot(aes(x = rh_median, y = slope, group = rh_median), size = 0.5, fatten = 0.8) +
  geom_line(aes(x = rh_median, y = slope, group = sensor, color = sensor, alpha = 0.9)) +
  ylim(c(0,1.2)) +
  facet_grid(~source) +
  ylab("Slope") + 
  ggtitle("SDS018") + 
  xlab("Relative humidity (%)") +
  customTheme

p_hpma<-filter(res_rh_temp, slope_p_value <= 0.05) %>%
  filter(grepl("HPMA115S0", sensor)) %>%
  ggplot() +    
  geom_boxplot(aes(x = rh_median,y = slope, group = rh_median), size = 0.5, fatten = 0.8) +
  geom_line(aes(x = rh_median, y = slope, group = sensor, color = sensor, alpha = 0.9)) +
  ylim(c(0,1.2)) +
  facet_grid(~source) +
  ylab("Slope") + 
  ggtitle("HPMA115S0") + 
  xlab("Relative humidity (%)") +
  customTheme


pl_sig<-plot_grid(p_pms, p_sps, p_hpma, p_sds, p_opcr1, ncol = 2)
p_sps
p_hpma
p_sds
p_opcr1
pl_sig

#ggsave(pl_sig, filename = "slope_evolution_sig.svg", width=200,height =200,units = "mm")

```


# R squared SIG with Box and Whisker

```{r}


p_pms<-filter(res_rh_temp,r_squared_p_value<=0.05) %>%
  filter(grepl("PMS5003",sensor)) %>%
  ggplot()+    
  geom_boxplot(aes(x = rh_median,y=r_squared,group=rh_median), size=0.5, fatten=0.8)+
      geom_line(aes(x = rh_median,y=r_squared, group = sensor, color = sensor,alpha=0.9))+

 ylim(c(0,1))+
  facet_grid(~source)+theme_bw()+ylab("r_squared") + ggtitle("PMS5003") + xlab("Relative humidity (%)")+theme(legend.position = "none", axis.title.x=element_blank(), axis.title.y=element_blank(), plot.title = element_text(hjust = 0.5))
p_pms 
p_opcr1<-filter(res_rh_temp,r_squared_p_value<=0.05) %>%
  filter(grepl("OPCR1",sensor)) %>%
   ggplot()+    
 geom_boxplot(aes(x = rh_median,y=r_squared,group=rh_median), size=0.5, fatten=0.8)+
      geom_line(aes(x = rh_median,y=r_squared, group = sensor, color = sensor,alpha=0.9))+
     ylim(c(0,1))+
  facet_grid(~source)+theme_bw()+ylab("r_squared") + ggtitle("OPCR1") + xlab("Relative humidity (%)")+theme(legend.position = "none", axis.title.y=element_blank(), plot.title = element_text(hjust = 0.5))

p_sps<-filter(res_rh_temp, r_squared_p_value<=0.05) %>%
  filter(grepl("SPS030",sensor)) %>%
   ggplot()+    
 geom_boxplot(aes(x = rh_median,y=r_squared,group=rh_median), size=0.5, fatten=0.8)+
      geom_line(aes(x = rh_median,y=r_squared, group = sensor, color = sensor,alpha=0.9))+
   ylim(c(0,1))+
  facet_grid(~source)+theme_bw()+ylab("r_squared") + ggtitle("SPS030")+xlab("Relative humidity (%)")+theme(legend.position = "none", axis.title.x=element_blank(), axis.title.y=element_blank(), plot.title = element_text(hjust = 0.5))


p_sds<-filter(res_rh_temp, r_squared_p_value<=0.05) %>%
  filter(grepl("SDS018",sensor)) %>%
   ggplot()+    
  geom_boxplot(aes(x = rh_median,y=r_squared,group=rh_median), size=0.5, fatten=0.8)+
    geom_line(aes(x = rh_median,y=r_squared, group = sensor, color = sensor,alpha=0.9))+
   ylim(c(0,1))+
  facet_grid(~source)+theme_bw()+ylab("r_squared") + ggtitle("SDS018") + xlab("Relative humidity (%)")+theme(legend.position = "none", axis.title.x=element_blank(), axis.title.y=element_blank(), plot.title = element_text(hjust = 0.5))

p_hpma<-filter(res_rh_temp, r_squared_p_value<=0.05) %>%
  filter(grepl("HPMA115S0",sensor)) %>%
  ggplot()+    
  geom_boxplot(aes(x = rh_median,y=r_squared,group=rh_median), size=0.5, fatten=0.8)+
      geom_line(aes(x = rh_median,y=r_squared, group = sensor, color = sensor,alpha=0.9))+
   ylim(c(0,1))+
  facet_grid(~source)+theme_bw()+ylab("r_squared") + ggtitle("HPMA115S0") + xlab("Relative humidity (%)")+theme(legend.position = "none", axis.title.x=element_blank(), axis.title.y=element_blank(), plot.title = element_text(hjust = 0.5))


pl_sig<-plot_grid(p_pms, p_sps, p_hpma, p_sds, p_opcr1, ncol = 2)
p_sps
p_hpma
p_sds
p_opcr1
pl_sig

#ggsave(pl_sig, filename = "r_squared_evolution_sig.svg", width=200,height =200,units = "mm")

```



