---
title: "Table 4, A7 and Figure A15- Coefficient of variation"
output: html_notebook
---

Table 4. Coefficient of variation obtained by the different models of sensors for different sources and
different variations of PM sources where n is the number of unit of each model used for the calculation
and k is the number of data points available.

Figure A15. Coefficient of variation obtained by the different models of sensors for the different
experiment, the different sources and different variations of PM sources.

```{r setup, message=FALSE, warning=FALSE, include=FALSE}

require(dplyr)
require(tidyr)
require(splitstackshape)
require(openair)
require(magrittr)
require(ggplot2)
require(plotly)
require(data.table)
require(zoo)
source("utilities.R")
source("variables.R")

```

```{r}

df_corr<- prepare_sensor_data(sensor_delay_corrected, cdt)%>%
    filter(!(sensor %in% c("HPMA115S0-T0B190900598", "PMS5003-2019031806703", "HPMA115S0-R0B174843287", "OPCR1-178872108","PMS5003-2019042601208")))

df<- prepare_sensor_data(sensor_raw_file, cdt)%>%
    filter(!(sensor %in% c("HPMA115S0-T0B190900598", "PMS5003-2019031806703", "HPMA115S0-R0B174843287", "OPCR1-178872108","PMS5003-2019042601208")))

df_dusttrak <- prepare_dusttrak_data(dusttrak_file, cdt) 


df_ref <- cSplit(indt = df, splitCols = c("sensor"), sep = "-", direction = "wide", drop = FALSE) %>%
    select(-sensor_2, -sensor_3)
  
  
df_ref_cor<-cSplit(indt=df_corr,splitCols = c("sensor"),sep="-",direction="wide",drop=FALSE) %>%
    select(-sensor_2,-sensor_3)
```


```{r Calculation used in the paper}



res<-df_ref %>%
  filter(sensor != "SHT35") %>%
  filter(exp != "") %>%
  group_by(date, sensor_1, source, variation) %>%
 summarise(sd = sd(PM25, na.rm = TRUE),count = n(),PM25_mean = mean(PM25,na.rm=TRUE))%>% 
  filter(sd!=0) %>% #Work (checked)
  mutate(CV = sd/PM25_mean ) %>%
  mutate(sum_cv_squared = CV*CV*(count-1)) %>%
  ungroup() %>%
  group_by(sensor_1, source, variation) %>%
  summarise(sqrt(sum(sum_cv_squared,na.rm=TRUE)/sum(count-1)),n(),mean(count))
res
#write.csv(res,"test_cv_niosh.csv")


```

```{r Same on corrected data}
res<-df_ref_corr %>%
  filter(sensor != "SHT35") %>%
  filter(exp != "") %>%
  group_by(date, sensor_1, source, variation) %>%
 summarise(sd = sd(PM25, na.rm = TRUE),count = n(),PM25_mean = mean(PM25,na.rm=TRUE))%>% 
  filter(sd!=0) %>% #Work (checked)
  mutate(CV = sd/PM25_mean ) %>%
  mutate(sum_cv_squared = CV*CV*(count-1)) %>%
  ungroup() %>%
  group_by(sensor_1, source, variation) %>%
  summarise(sqrt(sum(sum_cv_squared,na.rm=TRUE)/sum(count-1)),n(),mean(count))
res

```

```{r}
res<-df_ref %>%
  filter(sensor != "SHT35") %>%
  filter(exp != "") %>%
  group_by(date, sensor_1, source, variation, exp) %>%
 summarise(sd = sd(PM25, na.rm = TRUE),count = n(),PM25_mean = mean(PM25,na.rm=TRUE))%>% 
  filter(sd!=0) %>% #Work (checked)
  mutate(CV = sd/PM25_mean ) %>%
  mutate(sum_cv_squared = CV*CV*(count-1)) %>%
  ungroup() %>%
  group_by(sensor_1, source, variation, exp) %>%
  summarise(CV=sqrt(sum(sum_cv_squared,na.rm=TRUE)/sum(count-1)),k=n(),n=mean(count))

p<-res %>%
  filter(exp != "") %>%
  filter(source!="")%>%
  mutate(source_variation = paste0(source, "\n", variation)) %>%
  ggplot()+
  geom_point(aes(x=source_variation, y = CV))+
  facet_grid(exp~sensor_1)+
  theme_bw() +
  ylab("Coefficient of variation")+xlab("Sensor model")+theme(strip.text.y = element_text(size = 6), axis.text.x = element_text(size = 6))
p
#ggsave(p,filename = "cv_per_source_variation_exp.svg", height = 7, width = 8)
```



```{r}

df_corr %>%
  ungroup() %>%
  filter(sensor=="PMS5003-2019031806704") %>%
  ggplot()+geom_line(aes(x=date,y=PM25,group=sensor))+geom_line(data = filter(df,sensor=="PMS5003-2019031806704"), aes(x=date,y=PM25,colour="red"))->p

ggplotly(p, dynamicTicks = TRUE)


```


# On the calibrated data


```{r}


source("utilities.R")
source("variables.R")

res_rh_temp<-read.csv("C:/GitHub/AQ_analysis_lab/lm_no_enclosure_cdt_corr.csv")

df <- prepare_sensor_data(sensor_delay_corrected_20190905,cdt_corrected)

head(res_rh_temp)


df %>% inner_join(select(res_rh_temp, sensor, exp, source, slope, intercept, slope_p_value), by = c("sensor", "exp", "source")) -> df_coeff

df_coeff %>% 
  group_by(sensor) %>%
  mutate(PM25_corr = ifelse(slope_p_value<=0.05,(PM25-intercept)/slope), -999) %>%
  filter(PM25_corr != -999) -> df_calibrated
require(trelliscopejs)
df_calibrated %>%
ggplot(aes(x = date, y = PM25_corr)) + geom_line() + facet_trelliscope(exp~sensor,ncol=5)


dusttrak <- prepare_dusttrak_data(dusttrak_file, cdt_corrected)
require(splitstackshape)
df2<-cSplit(indt=df_calibrated,splitCols = c("sensor"),sep="-",direction="wide",drop=FALSE)

df2 %>%
  select(-sensor_2,-sensor_3)->df_calibrated


res<-df_calibrated %>%
  filter(sensor != "SHT35") %>%
  filter(exp != "") %>%
  filter(PM25_corr>=0) %>%
  group_by(date, sensor_1, source, variation) %>%
 summarise(sd = sd(PM25_corr, na.rm = TRUE),count = n(),PM25_mean = mean(PM25_corr,na.rm=TRUE))%>% 
  filter(sd!=0) %>% #Work (checked)
  mutate(CV = sd/PM25_mean ) %>%
  mutate(sum_cv_squared = CV*CV*(count-1)) %>%
  ungroup() %>%
  group_by(sensor_1, source, variation) %>%
  summarise(CV = sqrt(sum(sum_cv_squared,na.rm=TRUE)/sum(count-1)),n(),mean(count))
res


res<-dcast(setDT(filter(res,source!="")), sensor_1 ~ source+variation, value.var = c("CV"))
res
write.csv(res,"CV_calibrated.csv")
```

The coefficient of variation increases after the calibration...

# On the data calibrated for all models of sensors.

```{r}

df <- prepare_sensor_data("C:/GitHub/AQ_analysis_lab/sensor_delay_corrected_20190905.rds", cdt_corrected)
dt <- prepare_dusttrak_data(dusttrak_file, cdt_corrected)

```

```{r}

df2<-cSplit(indt=df,splitCols = c("sensor"),sep="-",direction="wide",drop=FALSE)

df2 %>%
  select(-sensor_2,-sensor_3)->df

df %>%
  filter(date>=as.POSIXct("2018-08-28 00:00:00",tz="UTC")) %>% #before that the DustTrak was set to take a reading every min, and after every 10 seconds
  select(sensor, exp, source, date, PM25, sensor_1) %>%
  filter(sensor!="SHT35") %>%
  filter(exp!="") %>%
  filter(grepl("No Enclosure",exp)) %>%
  group_by(exp, source, sensor_1) %>%
  nest() -> tmp

tmp %>%
  dplyr::mutate(regression = map(data, ~clean_regression(df =.x,dusttrak = dt, 0))) %>%
  unnest(regression, .drop=TRUE)  ->res
res
require(stringr)
res %>%
  mutate(rh_chamber = str_split(exp, " ")[[1]][1],
         temp_chamber = str_split(exp, " ")[[1]][2]) ->tmp

df %>% inner_join(select(res, sensor_1, exp, source, slope, intercept, slope_p_value), by = c("sensor_1", "exp", "source")) -> df_coeff

df_coeff %>% 
  group_by(sensor) %>%
  mutate(PM25_corr = ifelse(slope_p_value<=0.05,(PM25-intercept)/slope), -999) %>%
  filter(PM25_corr != -999) -> df_calibrated_sensor_model



res<-df_calibrated_sensor_model %>%
  filter(sensor != "SHT35") %>%
  filter(exp != "") %>%
  filter(PM25_corr>=0) %>%
  group_by(date, sensor_1, source, variation) %>%
 summarise(sd = sd(PM25_corr, na.rm = TRUE),count = n(),PM25_mean = mean(PM25_corr,na.rm=TRUE))%>% 
  filter(sd!=0) %>% #Work (checked)
  mutate(CV = sd/PM25_mean ) %>%
  mutate(sum_cv_squared = CV*CV*(count-1)) %>%
  ungroup() %>%
  group_by(sensor_1, source, variation) %>%
  summarise(CV = sqrt(sum(sum_cv_squared,na.rm=TRUE)/sum(count-1)),n(),mean(count))
res


res<-dcast(setDT(filter(res,source!="")), sensor_1 ~ source+variation, value.var = c("CV"))
res
write.csv(res,"CV_calibrated_sensor_model.csv")

```

Idem, it increases after calibration.

# CV according oto appendix C of https://www.cdc.gov/niosh/docs/2012-162/pdfs/2012-162.pdf 

```{r}


yi<-df_calibrated_sensor_model %>%
  filter(sensor != "SHT35") %>%
  filter(exp != "") %>%
  filter(PM25_corr>=0) %>%
  group_by(sensor, source, variation) %>%
 summarise(yi = sum(PM25)/n(), k =n())

yl<-df_calibrated_sensor_model %>%
  filter(sensor != "SHT35") %>%
  filter(exp != "") %>%
  filter(PM25_corr>=0) %>%
  group_by(date, source, variation, sensor_1) %>%
 summarise(yl = sum(PM25)/n(), u = n())


tmp<- df_calibrated_sensor_model %>%
   inner_join(yi, by=c("sensor", "source", "variation")) %>%
   inner_join(yl, by = c("date", "source", "variation", "sensor_1"))

 
yprim <-  tmp %>%
  group_by(date,sensor_1, source, variation) %>%
  summarise(yprim = sum(yi)/mean(u))
yprim
```